### 2020-12-15 README.Rmd
update readme image
update readme
commit changes requested by brad. supercript '+' in T-bet+ and link the cell surface protein atlas

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Single cell resolution landscape of equine peripheral blood mononuclear cells reveals diverse cell types including T-bet+ B cells."
```

<p align="center">
  <img width="460" height="300" src="https://github.com/BradRosenbergLab/equinepbmc/blob/307dec78c39ca7dec46d7c9235574fe2db82feec/analysis/data/derived_data/horse_DNA_image.jpg/460/300">
</p>

# Single cell resolution landscape of equine peripheral blood mononuclear cells reveals diverse cell types including T-bet+ B cells.

@@

> Roosheel Patel*, Joy E. Tomlinson*, Thomas J. Divers, Gerlinde R. Van de Walle, Brad Rosenberg, (2020). *Single cell resolution landscape of equine peripheral blood mononuclear cells reveals diverse cell types including T-bet+ B cells*. BMC Biology <https://doi.org/XXXX>

@@

> Roosheel Patel*, Joy E. Tomlinson*, Thomas J. Divers, Gerlinde R. Van de Walle, Brad Rosenberg, (2020). *Single cell resolution landscape of equine peripheral blood mononuclear cells reveals diverse cell types including T-bet+ B cells* biorxiv, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.1101/2020.05.05.077362>

@@

For surface annotation of differentially expressed genes, surface protein annotations were pulled from the Cell Surface Protein Atlas website {https://wlab.ethz.ch/cspa/#abstract}.

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Single cell resolution landscape of equine peripheral blood mononuclear cells reveals diverse cell types including T-bet<sup>+</sup> B cells."
```

  ![epbmclogo](analysis/data/derived_data/horse_DNA_image.png#style=centerme)

# Single cell resolution landscape of equine peripheral blood mononuclear cells reveals diverse cell types including T-bet<sup>+</sup> B cells.

@@

> Roosheel S. Patel*, Joy E. Tomlinson*, Thomas J. Divers, Gerlinde R. Van de Walle, Brad R. Rosenberg, (2020). *Single cell resolution landscape of equine peripheral blood mononuclear cells reveals diverse cell types including T-bet+ B cells*. BMC Biology <https://doi.org/XXXX>

@@

> Roosheel S. Patel*, Joy E. Tomlinson*, Thomas J. Divers, Gerlinde R. Van de Walle, Brad R. Rosenberg, (2020). *Single cell resolution landscape of equine peripheral blood mononuclear cells reveals diverse cell types including T-bet+ B cells* biorxiv, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.1101/2020.05.05.077362>

@@

For surface annotation of differentially expressed genes, surface protein annotations were pulled from the [Cell Surface Protein Atlas website](https://wlab.ethz.ch/cspa/#abstract).
